Supporting Information for: \\ Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-01-14 paper/arxiv/supp_1_head.tex
fix date and insert author in SI

% Title and Authors (Affiliations)

% Title
\title{Convolutional Neural Networks and Volcano Plots:
Screening and Prediction of Two-Dimensional Single-Atom Catalysts
for CO\textsubscript{2} Reduction Reactions}

@@

>>>>

% SI title
\title{Supporting Information for:  \\
Convolutional Neural Networks and Volcano Plots:
Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions}

@@

% Date
\date{January 15, 2024}
